### 2018-04-17 paper/paper.tex
update the answer 2.2.3.2

\documentclass[a4paper]{article}
\usepackage{amsmath, amssymb, bm}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\begin{document}
\begin{titlepage}
  \centering
    {\huge \bf Assignment 1\par}
    \vspace{1cm}
    {\Large Computational Intelligence, SS2018\par}
    \vspace{1cm}
    \begin{tabular}{|l|l|l|}
      \hline
      \multicolumn{3}{|c|}{\textbf{Team Members}}   \\ \hline
      Last name & First name & Matriculation Number \\ \hline
      Lee       & Eunseo     & 11739623             \\ \hline
      Shadley   & Alex       & 11739595             \\ \hline
      Lee       & Dayeong    & 11730321             \\ \hline
    \end{tabular}
\end{titlepage}

\section{Linear Regression}
\subsection{Derivation of Regularized Linear Regression}
\begin{itemize}
  \item Preliminary questions
    \begin{itemize}
      \item for each i, \(\bm{X}^{(i)}\) is n+1 dimensional column vector. For
        notaion convenience, all \(\bm{X}_0^{(i)}\) is set to \(0\).
      \item The gradient of \(J(\bm{\theta})\) is \[
          \frac{\partial J(\bm{\theta})}{\partial \bm{\theta}} = \langle
          \frac{\partial J(\bm{\theta})}{\partial \theta_0}, \quad
          \frac{\partial J(\bm{\theta})}{\partial \theta_1}, \quad
          \cdots, \quad
          \frac{\partial J(\bm{\theta})}{\partial \theta_n}
          \rangle
        \]. It is n+1 dimensional column vector.
      \item In gradient, function \(f\) is
        \(\mathbb{R}^n\rightarrow\mathbb{R} \) and the gradient itself is vector.
        The jacobian matrix of function
        \(\bm{f}\colon\mathbb{R}^n\rightarrow\mathbb{R}^m\) is
        \[[
          \quad \frac{\partial \bm{f}}{\partial x_1} \quad
          \frac{\partial \bm{f}}{\partial x_2} \quad
          \cdots \quad \frac{\partial \bm{f}}{\partial x_n} \quad
          ] =
          \begin{bmatrix}
            \frac{\partial f_1}{\partial x_1} & \cdots & \frac{\partial f_1}{\partial x_n} \\
            \vdots & \ddots & \vdots \\
            \frac{\partial f_m}{\partial x_1} & \cdots & \frac{\partial f_m}{\partial x_n}
          \end{bmatrix}
          \]
          where \(\bm{f} = <f_1, f_2, \cdots, f_m>\) and \(\bm{x} = <x_1, x_2, \cdots, x_n>\).
          When \(m=0\), Jacobian matrix and gradient are same.
        \item \(\bm{X\theta}\) is \(m\) dimension vector. The dimension of jacobian
          matrix \(\frac{\partial \bm{X\theta}}{\partial \bm{\theta}}\) is \(n+1 \times m\).
          In this case, \(\frac{\partial \bm{X\theta}}{\partial \bm{\theta}}\) is same with \(\bm{X}\).
    \end{itemize}
  \item 2
  \item 3
\end{itemize}

@@

\paragraph
4
\paragraph
5 One possible way to terminate the gradient descent is setting a threshold to the cost function. While caluating the cost in each iteration, if it is below the setting threshold, it can terminate the process. Using this way, it can not reach the perfect local minima but it can reach close to the local minima depending on the threshold. Therefore it can save time. If high accuracy is aimed, then set the threshold low. And if middle accuracy and high speeed are aimed, then set the threshold a little bit higher.
\subsubsection{Adaptative gradient descent (GDad)}
\paragraph
1 The following plots demonstrate the results of Logistic Regression with iterations = 1000, learning rate $\eta$ = 1 and varying degrees $l$ = \{1, 2, 5, 15\}:

>>>>

\documentclass[a4paper]{article}
\usepackage{amsmath, bm}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\begin{document}
\begin{titlepage}
	\centering
	{\huge \bf Assignment 1\par}
	\vspace{1cm}
	{\Large Computational Intelligence, SS2018\par}
	\vspace{1cm}
	\begin{tabular}{|l|l|l|}
	\hline
	\multicolumn{3}{|c|}{\textbf{Team Members}}   \\ \hline
	Last name & First name & Matriculation Number \\ \hline
	Lee       & Eunseo     & 11739623             \\ \hline
	Shadley   & Alex       & 11739595             \\ \hline
	Lee       & Dayeong    & 11730321             \\ \hline
	\end{tabular}
\end{titlepage}

\section{Linear Regression}
\subsection{Derivation of Regularized Linear Regression}
asdfasdf

@@

\paragraph
4
\paragraph
5

\subsubsection{Adaptative gradient descent (GDad)}
\paragraph
1 The following plots demonstrate the results of Logistic Regression with iterations = 1000, learning rate $\eta$ = 1 and varying degrees $l$ = \{1, 2, 5, 15\}:
